\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}
\title {}{\textbf{ Improve Your Fantasy Premier League Team.}}
\section{Introduction} 
	Fantasy Premier League is a gsme in which participants assemble an immaginary team of real life footballers on a fixed budget of 100m and score points based on those players actual statistical performances.Friends,Family and work mates play out for the ultimate prizes rewarded to the best manager at the end of the season.
	

\section{Objectives.}
To improve the managers overrall performance by raising theor weekly game rank and average high consistent point outcome.

\section{Findings On Your Research.}
	With over 4 million players, FPL is the biggest fantasy football game in the world.
FPL points are mostly based on statistical performance like cleansheets goals and assists so footballers like defensive midfielders whose game is entirely built on interceptions,possesion and tackles tend to be avoided since they have a low point return.
Every manager is only entitled to one transfer per game week.
Every manager is given the following chips:
\\
Benchboost- the substitutes points are counted too and its active once a season.
\\
Triple Captain – the captains points are tripled also active once a season
\\
All out attack – manager plays more attackers than defenders also ative once a season.
\\
Wild card – Allows the manager to make an infinity number of substitutes with out point cuts and is   availbale twice a season.

\section{Recommendations.}
To always follow forums and TV shows about the premier league to be aware of injuries,postponed matches or suspended players , this reduces points lost due to unavailable players.
\\
To make sure your team has the most owned players in the league to maintain consistency with others.
\\
To pick out a few differential players who will help you get ahead of your friends.
\\
To  always be patient and sign players because of their future point projection and not the points they already scored.
\\
To utilize the chips like benchboost and triple captain wisely to get a head of competing lot.

\section{Conclusion.}
If the above recommendationsare studied and followed carefully, the managers weekly rank and team management will greatly improve.
\end{document}
